### 2021-07-10 docs/manuscript/manuscript.tex
Update manuscript.tex

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Elucidating multi-input processing 3-node gene regulatory
network topologies capable of generating striped gene expression patterns}
% Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Juan Camilo Arboleda-Rivera\textsuperscript{1*},
Gloria Machado-Rodríguez\textsuperscript{1},
Boris Rodríguez-Rey\textsuperscript{2},
Jayson Gutiérrez\textsuperscript{3},
% Name5 Surname\textsuperscript{2\ddag},
% Name6 Surname\textsuperscript{2\ddag},
% Name7 Surname\textsuperscript{1,2,3*},
% with the Lorem Ipsum Consortium\textsuperscript{\textpilcrow}
\\
\bigskip
\textbf{1} Grupo de Fundamentos y Enseñanza de la Física y los Sistemas Dinámicos,
Instituto de Biología, Facultad de Ciencias Exactas y Naturales, Universidad de Antioquia
UdeA, Calle 70 No. 52-21, Medellín, Colombia.
\\
\textbf{2} Grupo de Fundamentos y Enseñanza de la Física y los Sistemas Dinámicos,
Instituto de Física, Facultad de Ciencias Exactas y Naturales, Universidad de Antioquia
UdeA, Calle 70 No. 52-21, Medellín, Colombia.
\\
\textbf{3} Flanders Marine Institute (VLIZ), Wandelaarkaai 7, 8400 Oostende,
Belgium
% \textbf{3} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\bigskip

@@

\subsection*{Background}
A central problem in developmental and synthetic biology is to understand the
mechanisms by which cells in a tissue or in a Petri dish process external cues
and transform such information into a coherent response, e.g. a terminal
differentiation state. It was long believed that this type of positional
information could be entirely attributed to a gradient of concentration of a
certain signaling molecule (i.e. a morphogen). However, advances in experimental
methodologies and computer modeling have demonstrated the crucial role of the
dynamics of a cell's gene regulatory network (GRN) in decoding the information
carried by the morphogen, which is eventually translated into a spatial
pattern. This morphogen interpretation mechanism has gained a lot of attention
in systems biology as a tractable system to investigate the emergent properties
of complex genotype-phenotype maps.

>>>>

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Elucidating multi-input processing 3-node gene regulatory
network topologies capable of generating striped gene expression patterns}
% Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Juan Camilo Arboleda-Rivera\textsuperscript{1*},
Gloria Machado-Rodríguez\textsuperscript{1},
Boris A. Rodríguez\textsuperscript{2},
Jayson Gutiérrez\textsuperscript{3},
% Name5 Surname\textsuperscript{2\ddag},
% Name6 Surname\textsuperscript{2\ddag},
% Name7 Surname\textsuperscript{1,2,3*},
% with the Lorem Ipsum Consortium\textsuperscript{\textpilcrow}
\\
\bigskip
\textbf{1} Grupo de Fundamentos y Enseñanza de la Física y los Sistemas Dinámicos,
Instituto de Biología, Facultad de Ciencias Exactas y Naturales, Universidad de Antioquia
UdeA, Calle 70 No. 52-21, Medellín, Colombia.
\\
\textbf{2} Grupo de Fundamentos y Enseñanza de la Física y los Sistemas Dinámicos,
Instituto de Física, Facultad de Ciencias Exactas y Naturales, Universidad de Antioquia
UdeA, Calle 70 No. 52-21, Medellín, Colombia.
\\
\textbf{3} Flanders Marine Institute (VLIZ), Wandelaarkaai 7, 8400 Oostende,
Belgium
% \textbf{3} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\bigskip

@@

\subsection*{Background}
A central problem in developmental and synthetic biology is understanding the
mechanisms by which cells in a tissue or a Petri dish process external cues
and transform such information into a coherent response, e.g., a terminal
differentiation state. It was long believed that this type of positional
information could be entirely attributed to a gradient of concentration of a
specific signaling molecule (i.e., a morphogen). However, advances in experimental
methodologies and computer modeling have demonstrated the crucial role of the
dynamics of a cell's gene regulatory network (GRN) in decoding the information
carried by the morphogen, which is eventually translated into a spatial
pattern. This morphogen interpretation mechanism has gained much attention
in systems biology as a tractable system to investigate the emergent properties
of complex genotype-phenotype maps.
